---
title: "DSST preprocessing"
author: "Pratik Bhandari"
date: "2019-07-19 (last edited: `r format(Sys.time())`)"
editor_options: 
  chunk_output_type: inline
output: 
    html_document:
        toc: yes
        toc_depth: 3
        number_sections: yes
---
TODO: Briefly explain the data type and data frame (columns, rows), dependent and independent variables. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE) #by default, all the code chunks below will be displayed when this markdown file is rendered.
```

# Initiate session

First, we load packages required for this project.

```{r setup1, include=TRUE, message=FALSE}
if(!require("pacman")) install.packages("pacman", repos = "http://cloud.r-project.org")
```

```{r setup2, include=TRUE, message=FALSE}
pacman::p_load(tidyverse, vroom, here, rprime, wrapr, data.table, ggthemes)
```

Then we import custom functions defined externally in a separate .R file.

```{r import_functions}
source(here("functions/dsst-functions.R")) #Imports custom functions
```

We imported `reduce_wm`, `msdminus`, and `msdplus` functions.
`reduce_wm` will be used to import eprime data file, while the latter two will be used in outlier removal. Outliers are operationalised as reaction times that are [mean±2SD].

# Import data

Create a list of all the txt files (i.e. eprime datafiles).
    
```{r fileimport, echo=TRUE}
files <- list.files(path = here("data","digitsymbol"), pattern = ".txt", full.names = T)
```

Use 'map_df' and the custom function defined above to create a mastersheet dataframe;`map_df` applies the function `reduce_wm` to all the txt files in the list 'files'.

```{r mastersheet, echo=TRUE}
mastersheet <- map_df(files, reduce_wm) %>% as_tibble(.)
write.csv(mastersheet, here("data/dsst-mastersheet-48pp.csv")) #Save this mastersheet as csv.
```

There was one data file for each participant as an output from eprime. This file "mastersheet" now contains the data from all the participants in a single dataframe. 

<!-- _Now you can work on this df 'mastersheet' with `tidyverse` for datawrangling purposes, filter columns and rows by conditions, subjects, etc. as and when required._ -->

# Clean and clear df columns

Check the column names:
```{r column_name}
colnames(mastersheet)
```

Now select only the required columns:
```{r filter_column, echo=TRUE}
mastersheet <- mastersheet %>% select(id = Eprime.Basename,
                                      trialNo = Sample,
                                      displayedList = Eprime.LevelName,
                                      stim_correctness = Correctness,
                                      expected_response = Correct,
                                      participant_response = StimulDS1.RESP,
                                      rt = StimulDS1.RT)
```

Change the class of some columns:
```{r column_class}
mastersheet$trialNo <- as.factor(mastersheet$trialNo)
mastersheet$rt <- as.numeric(mastersheet$rt)
```

# Add new columns for accuracy and ppID

First create a copy of mastersheet with a new column that has values 0 and 1 for incorr. and corr. responses. respectively to later calculate accuracy.

```{r corr_incorr}
dsst <- cbind.data.frame(mastersheet,
                           corrIncorr = with(mastersheet,
                                             ifelse(expected_response == participant_response, 1, 0)
                                             )
                           )

# dsst48
```

Auto-generated participant ids are not human readable. So, we'll extract easy-to-process ids.

```{r participant_id, echo=TRUE}
dsst <- dsst %>% #e.g.,`Digit Symbol-0111-1` will be broken into `Digit`, Symbol` and `0111`; `1` will be discarded:
    separate(id, c("expt.1", "expt.2", "idNumber"), extra = 'drop') %>%
    select(-expt.1, -expt.2) #Only select `0111`
dsst$idNumber <- str_replace_all(dsst$idNumber, "(^0)", "") #Remove leading zero. So, the id is `111`.
dsst$idNumber <- as.integer(dsst$idNumber) 
```

# Preparation for analysis

## RT distribution and visualisation

Based on the output of the `boxcox` function, rt might have to be transformed to log-, square- or other scale(s).

```{r distribution, echo=TRUE}
MASS::boxcox(rt ~ idNumber, data=dsst)
```

It seems, we could log transform the data.
Add a new column with transforming RT to log RT.

```{r log_transform}
dsst$lrt <- log10(dsst$rt)
dsst
```

(It's not a standard practice to log transform DSST data. So, for the moment, we'll continue with raw RT.)

## Outlier removal

```{r outlier, echo=TRUE, results='hide'}
upperlimit <- dsst %>% group_by(idNumber) %>% summarise(upperlimit=msdplus(rt))
lowerlimit <- dsst %>% group_by(idNumber) %>% summarise(lowerlimit=msdminus(rt))

dsst <- merge(dsst, upperlimit)
dsst <- merge(dsst, lowerlimit)

dsst_filtered <- dsst %>% filter(rt>lowerlimit & rt<upperlimit)
```

Filter out incorrect responses, and create a df for analyses.
```{r filter_acc}

dsst_filtered_inccorrect <- dsst_filtered %>% filter(corrIncorr==0) # This is the df of only incorrect responses
dsst_filtered_correct <- dsst_filtered %>% filter(corrIncorr==1) # This is the df of only correct responses; analyses on this.
dsst_dat <- dsst_filtered_correct #making a copy; for ease to remember and ease to work.
```

## Plots

To group the plots by age-group, factorize the 'group' column
```{r factorise_group}
dsst.dat$group <- as.factor(dsst.dat$group)
```

**Density plot**

```{r densityplot, fig.width=15}
cowplot::plot_grid(
 ggplot(data = dsst, aes(x=rt, color=group)) + geom_density() +
  xlab("Reaction time [ms]") +
  ylab("Number of responses") +
  ggtitle("...of all responses"),
 ggplot(data = dsst.dat, aes(x=rt, color=group)) + geom_density() +
  xlab("Reaction time [ms]") +
  ylab("Number of responses") +
  ggtitle("...after filtering"))

```


**Histogram and frequency polygons**

```{r, fig.width=15}
cowplot::plot_grid(ggplot(data = dsst, aes(x=rt, fill = group)) + geom_histogram(stat = "bin", bins = 75) + geom_freqpoly(stat = "bin", bins = 75) +
  xlab("Reaction time [ms]") +
  ylab("Number of responses") +
  ggtitle("...of all responses"), 
ggplot(data = dsst, aes(x=rt, fill = group)) + geom_histogram(stat = "bin", bins = 75) + geom_freqpoly(stat = "bin", bins = 75) +
  xlab("Reaction time [ms]") +
  ylab("Number of responses") +
  ggtitle("after filtering"))
```


# End

Get the session info.

```{r info, eval=FALSE}
sessionInfo()
```

Save the data.

```{r save, echo=TRUE, eval=FALSE}
save.image("dsst-v1.RData")
```
