---
title: "Sentence comprehension: Analyses"
author: "Pratik Bhandari"
date: "2020-07-20 (last revised: `r format(Sys.time())`)"
editor_options: 
  chunk_output_type: inline
output: 
    html_document:
        toc: yes
        toc_depth: 2
        number_sections: yes
---

TODO: Briefly explain the data type and data frame (columns, rows), dependent and independent variables. 

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE) #by default, all the code chunks below will be displayed when this markdown file is rendered.
```

# Initiate session

First, we load packages required for this project.

```{r setup2, include=TRUE, message=FALSE}
source(here::here("rmd-scripts", "load-packages.R"))
```

# Prepare df

We are continuing from the previous Rmd file (01_preprocessing.Rmd).

```{r}
load(here("rmd-scripts/01_crwdscng-v1.RData")
```

**Create a new df for GLMM.**


```{r}

# Setting df
dat.LM <- dat.LM[which(dat.LM$verb_acc=="1" & dat.LM$noiseband!='4'),] # This selects only verb-correct responses at 4-channel noise-vocoded speech
dat.LM <- droplevels(dat.LM) #We could directly have done `dat.LM <- dat.subj2.v` as well.

# Converting to factors with appropriate levels
dat.LM$cloze <- factor(dat.LM$cloze, levels = c("Low", "High"), labels = c("Low", "High"))
dat.LM$speed <- factor(dat.LM$speed, levels = c('normal', 'slow'), labels = c('Normal', 'Slow'))

# Setting appropriate contrasts
contrasts(dat.LM$cloze) <- contr.treatment(3) 
contrasts(dat.LM$speed) <- contr.treatment(3) 

```

## Create model matrix
```{r modelmatrix, cache=TRUE, eval=FALSE}
mm <- model.matrix(~ speed*cloze, data = dat.LM)

slow <- mm[,2];
hp <- mm[,3];
slow_hp <- mm[,4]
```

# Maximal model with zero cp
```{r zcp, eval=FALSE, cache=TRUE}
tic("model runtime");
zcp <- glmer(noun_acc.v ~ 1 + slow + hp + slow_hp +
        (1 + slow + hp + slow_hp || participants) + 
        (1 + slow + hp + slow_hp || itemNo), 
      data=dat.LM, family = "binomial", 
      control = glmerControl(calc.derivs = FALSE, optimizer="bobyqa", optCtrl = list(maxfun=1e6)),
      nAGQ = 0, na.action = na.exclude);
toc()
```
model runtime: `56.231` sec elapsed

This maximal model converges well.

**Predictability as continuous variable**

Run the same maximal model as in `zcp` model. Here, instead of using categorical variable `cloze`, use `cloze_prob`.

```{r cloze-probability, cache=TRUE}
tic("model runtime");
zcp_cloze <- glmer(noun_acc.v ~ 1 + cloze_prob*speed +
                  (1 + cloze_prob*speed || participants) + 
                  (1 + cloze_prob*speed || itemNo), 
                data=dat.LM, family = "binomial", 
                control = glmerControl(calc.derivs = FALSE, optimizer="bobyqa", optCtrl = list(maxfun=1e6)),
                nAGQ = 0, na.action = na.exclude);
toc()
```
model runtime: `1400.87` sec elapsed

The results are not different than using cloze as categorical variable.

# Check for adaptation

Participants may show listening effect, i.e. adaptation. Add trial number to the fixed effects structure to test this.

```{r adaptation-model}
tic("model runtime")
zcp_tn <- glmer(noun_acc.v ~ 1 + slow + hp + slow_hp + c_trialNo +
               (1 + slow + hp + slow_hp || participants) + 
               (1 + slow + hp + slow_hp || itemNo), 
             data=dat.LM, family = "binomial", 
             control = glmerControl(calc.derivs = FALSE, optimizer="bobyqa", optCtrl = list(maxfun=1e6)),
             nAGQ = 0, na.action = na.exclude)
toc()
```
model runtime: `46.112` sec elapsed


# End

Get the session info.

```{r info, eval=FALSE}
sessionInfo()
```

Save the data.

```{r save, echo=TRUE, eval=FALSE}
save.image("02_crwdscng-v1.RData")
```


