---
title: "Sentence comprehension: Summary plots"
author: "Pratik Bhandari"
date: "2020-07-29 (last revised: `r format(Sys.time())`)"
editor_options: 
  chunk_output_type: inline
output: 
    html_document:
        toc: no
---

TODO: Briefly explain the data type and data frame (columns, rows), dependent and independent variables. 

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE) #by default, all the code chunks below will be displayed when this markdown file is rendered.
```

**Initiate session**

First, we load packages required for this project.

```{r setup2, include=TRUE, message=FALSE}
source(here::here("rmd-scripts", "load-packages.R"))
```

We are continuing from the previous Rmd files (01_preprocessing.Rmd and 02_glmm.Rmd).

```{r}
load(here("rmd-scripts/02_crwdscng-v1.RData")
```

**Summary df 1**

Group and summarise with accuracy in percentages.

```{r df1, cache=TRUE}
dat.anv <- dat.subj2.v %>%  #recall that `dat.subj2.v` is the df that contains trials with verb correct responses
  group_by(participants,speed, cloze, listnumber) %>%
    summarise(totalCorr=sum(noun_corr1==1), totalIncorr=sum(noun_corr1==0)) %>%
      mutate(total=totalCorr+totalIncorr,
             accuracy=round(((totalCorr/(totalCorr+totalIncorr))*100), digits=2))
dat.anv <- droplevels(dat.anv)
```

Refactor and raname the factors for better interpretibility in the plot.

```{r df2, cache=TRUE}
dat.anv <- dat.anv %>% mutate(cloze=factor(cloze, levels = c("Low", "High"),
                                           labels = c("Low Predictability", "High Predictability")),
                              speed=factor(speed, levels = c("normal", "slow"),
                                           labels = c('Normal', 'Slow')))
```


**Summary df 2**

Create a df with mean and SE of accuracies across the conditions.

```{r}
dat.anv2 <- summarySEwithin(
  data = dat.anv,
  measurevar = 'accuracy',
  withinvars = c('speed', 'cloze'),
  idvar = 'participants'
) %>% 
  select(speed, cloze, N, accuracy, se) %>% 
  mutate(cloze=factor(cloze, levels = c("Low", "High"),
                      labels = c("Low Predictability", "High Predictability")),
       speed=factor(speed, levels = c("normal", "slow"),
                    labels = c('Normal', 'Slow')))
```


**Raincloudplot**

```{r}
ns_raincloud <-
ggplot(dat.anv, aes(x=speed,y=accuracy, fill=speed, group=speed))+
  geom_flat_violin(position = position_nudge(x = .3, y = 0),
                   adjust =2, trim =TRUE)+
  geom_point(position = position_jitter(width = .15),
             size = .9, alpha=.4, colour = "black")+
  geom_point(data = dat.anv2, #Create this df from `dat.anv`
             aes(x = speed, y = accuracy),
             position = position_nudge(.25))+
  geom_errorbar(data = dat.anv2, 
                aes(x = speed, y = accuracy,
                    ymin = accuracy-se, ymax = accuracy+se),
                position = position_nudge(.25), width = 0.1, size = 0.8)+
  geom_line(data = dat.summary_expt1,
            aes(x = speed, y = accuracy, group = cloze),
            position = position_nudge(.25),
            linetype = 1, size = 0.8)+
  theme_cowplot()+
  guides(fill = FALSE, colour = FALSE) +
  scale_fill_manual(#name="Target word\npredictability",
                    values = c("Normal"="#DCDCDC", "Slow" ="#808080")) +
  labs(#title = "Experiment 1: Slow vs Normal",
       x = "Speech rate", y = "Response accuracy",
       colour=" ")+
  facet_grid(~cloze) +
  theme(axis.text.x = element_text(size = 13),
        axis.text.y = element_text(size = 13),
        axis.title = element_text(size = 15),
        strip.text.x = element_text(size = 15))
```

# End

Get the session info.

```{r info, eval=FALSE}
sessionInfo()
```

Save the data.

```{r save, echo=TRUE, eval=FALSE}
save.image("03_crwdscng-v1.RData")
```

